\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-11 forwards-and-backwards.tex
Update on Overleaf.

%%%%%%%%%%
\paragraph{Fisher--KPP:}
A great deal more attention has been paid to the classical Fisher-KPP equation,
\begin{align} \label{eqn:fkpp}
    v_t = v_{xx} + v (1-v) .
\end{align}
In this case,
even though we do not have an explicit formula for the wave shape,
these methods give us information about ancestral lineages.
The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
but started from any compact perturbation of a Heaviside function, the 
solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
\cite{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
No matter what the initial condition,
for any $t>0$ the support of the 
solution will be the whole real line. 
Since in ths case, $r = \gamma = 1$,
the generator of the motion of an ancestral lineage is
$$
    \Lgen \phi
    =
    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
$$
Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
so the motion of the lineage is close to Brownian motion.
On the other hand, for $x < 0$ the lineage behaves approximately as
Brownian motion with drift at rate two to the right.
This implies that
ancestral lineages are pushed into the tip of the wave,
and there is no stationary distribution.
These results agree with those of \comment{XXX}.

@@

With each level,
we can associate a Poisson random measure
$\Tilde{\Pi}$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
determines the birth times of the offspring of the particle at that level, the location of the
offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
location of the particle with level $U_{\tau}(t)$. 
Now $U_{\tau}$ satisfies
\begin{equation}
U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
\end{equation}
If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$. We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead. The (potential) new level is 
\begin{equation}\label{New birth potential level}
    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
\end{equation}
If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then 
\begin{equation}\label{eq: Individual Evolution Jump Kernel}
P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
\end{equation}
Consequently, 
$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
and 
$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
level. Consequently, for $t \geq \tau$
\begin{align}\label{eq: Spatial evolution of individual lineage}
X_{\tau}(\tau+t)=&X_{\tau}(t)\\
&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
\end{align}
Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$. Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$. When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$. When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$. As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.  Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$. If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\

@@

                    \frac{\epsilon^2_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}

@@

F(s)=  \frac{\epsilon^2_r }

@@

then 

@@

@@

        \leq  \theta \left(F\left(1 / \theta \right)-1\right) 
                \times \epsilon_\gamma^d \epsilon_r^{-d}
                p_{\epsilon^2_\gamma}(x-w),

@@

so we have our bound 
as $F(x)$ has bounded derivative in a neighbourhood around $0$.

We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have
\begin{align}
&\left\{
            \rho_r * \eta(y)
            -
            \rho_r * \eta(x)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \rho_r(y-w)
        -
        \rho_r(x-w)
    \right)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left(\rho_r * \eta(x)\right)^2 \left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw)
\right\}^2  \\
&\qquad
\le
\left(\rho_r * \eta(x)\right)^2 
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw) \\
&\qquad
=
\rho_r * \eta(x)
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \rho_r(x-w)
\eta(dw).
\end{align}
Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
\begin{equation}
\begin{aligned}
 \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
                   e^{-(x-w)^2(\frac{1}{\varepsilon^2_r}-\frac{1}{\varepsilon^2_\gamma})}
                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
\end{aligned}
\end{equation}
it suffices to show that 
\begin{equation}
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
\end{equation}
where
$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
q_{\theta}(x,dy).$$

\end{proof}
\begin{lemma}[Compact Containment for the population process]
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
    uniformly in $\theta$.
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that

\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$

>>>>

%%%%%%%%%%
\paragraph{Fisher--KPP:}
A great deal more attention has been paid to the classical Fisher-KPP equation,
\begin{align} \label{eqn:fkpp}
    v_t = v_{xx} + v (1-v) .
\end{align}
In this case,
even though we do not have an explicit formula for the wave shape,
these methods give us information about ancestral lineages.
The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
but started from any compact perturbation of a Heaviside function, the 
solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
\cite{kolmogorov/petrovsky/piscounov:1937,\meanqramson:1983}.
No matter what the initial condition,
for any $t>0$ the support of the 
solution will be the whole real line. 
Since in ths case, $r = \gamma = 1$,
the generator of the motion of an ancestral lineage is
$$
    \Lgen \phi
    =
    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
$$
Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
so the motion of the lineage is close to Brownian motion.
On the other hand, for $x < 0$ the lineage behaves approximately as
Brownian motion with drift at rate two to the right.
This implies that
ancestral lineages are pushed into the tip of the wave,
and there is no stationary distribution.
These results agree with those of \comment{XXX}.

@@

With each level,
we can associate a Poisson random measure
$\Tilde{\Pi}$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
determines the birth times of the offspring of the particle at that level, the location of the
offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
location of the particle with level $U_{\tau}(t)$. 
Now $U_{\tau}$ satisfies
\begin{equation}
U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
\end{equation}
If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$. We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead. The (potential) new level is 
\begin{equation}\label{New birth potential level}
    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
\end{equation}
If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then 
\begin{equation}\label{eq: Individual Evolution Jump Kernel}
P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
\end{equation}
Consequently, 
$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
and 
$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original

level. Consequently, for $t \geq \tau$
\begin{align}\label{eq: Spatial evolution of individual lineage}
X_{\tau}(\tau+t)=&X_{\tau}(t)\\
&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
\end{align}
Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$. Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$. When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$. When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$. As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.  Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$. If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\

@@

                    \frac{\epsilon^d_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}

@@

F(s)=  \frac{\epsilon^d_r }

@@

then $F(0)=0$ and

\begin{align}
F'(s)=&  -\frac{\epsilon^d_r |\covq|}
        {2\left|\covq s +  \epsilon^2_r I \right|^{3/2}}
        \exp \left(
                    \frac{(x-w-\meanq s)^{T}
                        (\covq s +  \epsilon^2_r I)^{-1}
                        (x-w-\meanq s)}{2}
                        -\frac{|x-w|^2}{2\epsilon^2}
            \right)\\
    &+\frac{\epsilon^d_r }
        {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
        \exp \left(
                    \frac{(x-w-\meanq s)^{T}
                        (\covq s +  \epsilon^2_r I)^{-1}
                        (x-w-\meanq s)}{2}
                        -\frac{|x-w|^2}{2\epsilon^2}
            \right) \\
    & \qquad \times \frac{1}{2}
                    \bigg\{
                         -\meanq^{T}(\covq s + \epsilon^2_r I)^{-1}(x-w-\meanq s)\\
    & \qquad \qquad     -(x-w-\meanq s)^{T}
                        (\covq s +  \epsilon^2_r I)^{-1}\meanq\\
    & \qquad \qquad     -(x-w-\meanq s)^{T}
                        \covq(\covq s +  \epsilon^2_r I)^{-2}(x-w-\meanq s)                    
                    \bigg\},
\end{align}
which is continuous and bounded near $s=0$.
As a result,
\begin{align}
\left| \theta \int_{\mathbb{R}^d}
                \left(p_{\epsilon^2_r}(y-w)
                        -p_{\epsilon^2_r}(x-w)
                \right)
                q_\theta(x,dy)
        \right|
        \leq&  \theta \left(F\left(1 / \theta \right)-1\right) 
                \times \epsilon_\gamma^d \epsilon_r^{-d}
                p_{\epsilon^2_\gamma}(x-w)\\
         =&  F'(u) 
                \times \epsilon_\gamma^d \epsilon_r^{-d}
                p_{\epsilon^2_\gamma}(x-w)        
\end{align}
for some $u \in [0, 1/\theta]$ by Intermediate Value Theorem. We have therefore established our bound as $F(s)$ has bounded derivative in a neighbourhood around $0$.

We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have

@@

&\left\{
            \rho_r * \eta(y)
            -
            \rho_r * \eta(x)
\right\}^2  \\
&\qquad
\int
    \left(
        \rho_r(y-w)
        -
        \rho_r(x-w)

@@

\eta(dw)
\right\}^2  \\
&\qquad
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
\left(\rho_r * \eta(x)\right)^2 \left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw)
\right\}^2  \\
&\qquad
\le
\left(\rho_r * \eta(x)\right)^2 
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw) \\
&\qquad
\rho_r * \eta(x)
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \rho_r(x-w)
\eta(dw).

@@

Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
    \label{eq: gamma-r convolution comparison}
 \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
                   e^{-(x-w)^2(\frac{1}{\epsilon^2_r}-\frac{1}{\epsilon^2_\gamma})}
                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
it suffices to show that 
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
q_{\theta}(x,dy).$$
Writing out $H$,
H_\theta(x, w)
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
                ||y - w||^2 - ||x - w||^2
            \right\}
        -
        1
        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dy.
Writing $z=y-x-\meanq$, we have that 
||y - w||^2 - ||x - w||^2 
=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
As a result, we have 
H_\theta(x, w)
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
            \right\}
        -
        1
        e^{-\theta z^{T}\covq^{-1}z  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\
=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \times \int
        \exp\left(
            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
            - \frac{1}{\epsilon_r^2} ||z||^2
            e^{-\theta z^{T}\covq^{-1}z  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\ \label{eq: Second moment term matrix calculation}
&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \qquad \qquad \times     \int
    \frac{ \exp\left(
             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
              -\frac{1}{2\epsilon_r^2} ||z||^2
            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
dz\\
&+1.
We now consider the integral of the form 
\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz   
for $v \in \mathbb{R}^d$ and $C>0$. 
We have 
&\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\
=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
dz\\
=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
\exp 
\left(
\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
\right),
where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.

Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
and $C=\frac{1}{\epsilon_r^2}$,
we have the expression in Equation
\eqref{eq: Second moment term matrix calculation} is 
$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right).$$
Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
and $C=\frac{1}{2\epsilon_r^2}$,
we have the expression in Equation
\eqref{eq: first moment term matrix calculation} is 
$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right).$$
As a result, we have 
\begin{align*}
&H_{\theta}(x,w)\\
=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right)\\
&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
\right)\\
&+1.
\end{align*}
If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
\begin{align*}
&F(s)\\
=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
\exp 
\left(
\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
\right)\\
&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
\exp 
\left(
\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
\right)\\
&+1\\
&=G_1(s)+2G_2(s)+1
\end{align*}
we can check that $F(0)=0$.
As a result, 
$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
for some $s \in [0, 1/\theta]$.

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
\begin{align} \label{eqn:goal3}
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

We consider how to differentiate function $G$ of the form 
$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.

Since 
\begin{equation}
\begin{aligned}
G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
                            - sv^{T}BC(I+Cs)^{-2}v
                    \right\}\\
      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
        \right)\\
      & \qquad \times
        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
\end{aligned}
\end{equation}
using non-negativity of $A,B,C$ we have
\begin{equation}
\label{eq: bounds on G'}
|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
\end{equation}
As a result, we have that 
\begin{equation}
\label{eq: bounds on G}
G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}.    
\end{equation}

Finally note that, 
$$F'(s) \leq G_1'(s)+2G_2'(s),$$
where 
$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
and 
$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
Substituting these quantities on Equation \eqref{eq: bounds on G'} and Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
\end{proof}

\begin{lemma}[Compact Containment for the population process]
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
    uniformly in $\theta$.
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$
